Making Sequential Programs Deterministic

### 2019-03-22 introduction.tex
Edits in introduction

The high-level goal of our work is to provide programmers with a tool for
specifying deterministic properties in a program and verifing them
at compile time.

@@

We have defined a type system with three types\todo{reference a figure}:
\<Det> represents values that will be the same across executions,
\<OrderNonDet> represents collections that are guaranteed to contain the same elements albeit in possibly
different iteration order, and
\<NonDet> provides no determinism guarantees:  it represents values that
might differ from run to run.
Programmers can write these types to specify their program's behavior.
Our type system contains a variety of other features that increase
expressiveness and reduce false positive alarms.\todo{reference a section}

We have implemented this type system in the context of Java.
We annotated all the collection
classes (Lists, Sets and Maps) in the JDK with our new type system.

@@

This paper makes the following contributions:
\begin{enumerate}
	\item We provide a design and implementation of a type system for expressing deterministic properties in sequential programs.
	\item We annotated several classes in JDK. By doing this, we have translated the specification for these APIs from
	human readable comments to machine readable and verifiable documentation.
	\item We performed a case study of a real world java program Randoop (loc, etc) which revealed bugs.
	\item We perform a comparative study of our technique with state of the art flaky test detectors and present results.
\end{enumerate}

% LocalWords:  NONDEX NonDex DeFlaker

>>>>

The high-level goal of our work is to provide programmers with a tool for
specifying deterministic properties in a program and verifying them
at compile time.

@@

Our analysis uses three main abstractions, or approximations to run-time values:
\begin{description}
\item[\<Det>] represents values that will be the same across executions.
\item[\<OrderNonDet>] represents collections that are guaranteed to contain the same elements albeit in possibly
different iteration order.
\item[\<NonDet>] represents values that
might differ from run to run.
\end{description}
\noindent
Programmers can write these to specify their program's behavior.
Our type system contains a variety of other features that increase
expressiveness and reduce false positive alarms.\todo{reference a section}

We have implemented this analysis as a pluggable type system for Java.

@@

This paper makes the following contributions:
\begin{enumerate}
  \item We designed a type type system for expressing determinism properties.

  \item We implemented the type system for Java.

  \item In a case study, we annotated several libraries, including the
    relevant parts of the JDK (Java's standard library).  This provides a
    formal, machine-readable specification for the libraries, and it
    demonstrates the richness of our type system.

  \item In another case study, we ran our analysis on a 24 KLOC project that
    developers had spent weeks of effort to make deterministic.  Our system
    discovered nondeterminism that the developers had overlooked, and they
    accepted our patches.

  \item We compared our tool against state-of-the-art flaky test
    detectors.\todo{Say something about the results.}
\end{enumerate}

% LocalWords:  NONDEX NonDex DeFlaker Det OrderNonDet NonDet
